Women highest Level Education in 20 years

### 2023-03-14 outputs/paper/paper.qmd
Update
Redid some graphs

---
title: "Women highest Level Education in 20 years"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

@@

>>>>

---
title: "Women highest Level Education in 20 years"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
hello
---

@@

merged_gss <- read.csv(here::here("outputs/data/merged_gss.csv"))

@@

```{r}
library(tidyverse)

## mean education level over 20 yrs ##

merged_gss |> group_by(Year) |> summarize(mean= mean(Highest_Educ_Level, na.rm = TRUE)) |>
  ggplot(aes(x = Year, y = mean)) +
  geom_line(group = 1) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Mean highest education level of Women over 20 Years",
    x = "Year",
    y = "Mean Educ Level %"
  )

```
```{r}
library(tidyverse)

## mean occ. prestige pct over 20 years ##

merged_gss |> group_by(Year) |> summarize(mean = mean(Occupational_Prestige_Pct, na.rm = TRUE)) |>
  ggplot(aes(x = Year, y = mean)) +
  geom_line(group = 1) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Occupational Prestige of Women over 20 Years",
    x = "Year",
    y = "Mean Occ. Prest. %"
  )

merged_gss |> group_by(Year) |> count(Happiness) |>
  ggplot(aes(x = Year, y = n, fill = Happiness)) +
  geom_col(position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Womens Happiness over 20 Years",
    x = "Year",
    y = "Count"
  )
```
